### 2024-10-30 Manuscript/main_ecography_R1.tex
Update main_ecography_R1.tex

\begin{table}
\center
\scriptsize
\begin{tabular}{p{0.2\linewidth}|p{0.2\linewidth}|p{0.4\linewidth}|p{0.2\linewidth}}
\textbf{Approximated mechanism (biological)} & \textbf{Used mechanism (algorithm in \texttt{dispRity::reduce.space})} & \textbf{Stressor description} & \textbf{Type of metric expected to recover the mechanism}\\
\hline
  Null mechanism & Random removal (``random'') & No overall change in observations' traits or community structure except for the reduction in the number of observations. & Metrics sensitive to the amount of data \\
  Equalising fitness & Size change (``size'') & When observations with trait combinations that are more extreme (i.e. observations located away from the centre of the trait space) are disadvantaged due to some resource concentration gradient. & Metrics capturing changes in richness (but not divergence and regularity) \\
  Facilitation & Density change (``density'') & When observations with closely shared trait combinations (i.e. located close together in the trait space) are more likely to survive the stressor. In other words, this simulates the idea that some observations are more likely to be resilient if they are present in a community of observations (e.g. a community of species) with shared traits rather than the opposite. & Metrics capturing changes in regularity (but not richness and regularity) \\
  Environmental filtering & Position change (``position'') & When an increase in observations' trait similarity happens through some strong abiotic constraints \citep{cornwell2006trait}. For example, some trait combinations become more and more unlikely due to some environmental constraints (i.e. some regions of the trait space become unsuitable). & Metrics capturing changes in position (and richness) \\\\
  Competitive exclusion & Evenness change (``evenness'') & When functionally similar observations compete more intensively with one another than with functionally dissimilar observations (``competitive exclusion principle''; \citealt{hardin1960competitive}). At the extreme, it implies that only dissimilar individuals will coexist (``limiting similarity principle''; \citealt{macarthur1967limiting}). & Metrics capturing changes in divergence (but not richness and regularity) \\\\

@@

For the empirical data, we see again a range of different possible interpretations depending on the metric describing the pattern.
For example, all richness metrics (green; Figure \ref{Fig:empirical_results}) pick up a similar relative increase (i.e., relative to the null stressor) in richness for both the historic and extant datasets.
However, the results are occasionally contrasting between the historical and extant datasets, with a respective decrease and increase with some divergence metrics (e.g. functional dispersion based on dendrograms or hypervolumes).
Finally, some metrics pick up a decrease for both datasets (e.g. functional evenness based on hypervolumes - although the 95\% confidence intervals overlapped with 0).
Note that this apparent global increase in most metric values may appear counter intuitive given that 46\% and 69\% of species went extinct over the two time periods.
This is due to the scaling of the metrics compared to random equivalent extinctions.
That is, Figure \ref{Fig:empirical_results} is not displaying absolute changes in trait space occupancy but rather changes in trait space occupancy relative to a crude neutral model where all species are equally likely to go extinct.

>>>>

\begin{table}
\center
\scriptsize
\begin{tabular}{p{0.2\linewidth}|p{0.2\linewidth}|p{0.4\linewidth}|p{0.2\linewidth}}
\textbf{Approximated mechanism (biological)} & \textbf{Used mechanism (algorithm in \texttt{dispRity::reduce.space})} & \textbf{Stressor description} & \textbf{Type of metric expected to recover the mechanism}\\
\hline
  Null mechanism & Random removal (``random'') & No overall change in observations' traits or community structure except for the reduction in the number of observations. & Metrics sensitive to the amount of data \\
  Equalising fitness & Size change (``size'') & When observations with trait combinations that are more extreme (i.e. observations located away from the centre of the trait space) are disadvantaged due to some resource concentration gradient \citep{chesson2000mechanisms,barot2004mechanisms}. & Metrics capturing changes in richness (but not divergence and regularity) \\
  Facilitation & Density change (``density'') & When observations with closely shared trait combinations (i.e. located close together in the trait space) are more likely to survive the stressor \citep{bruno2003inclusion, danet2024species}. In other words, this simulates the idea that some observations are more likely to be resilient if they are present in a community of observations (e.g. a community of species) with shared traits rather than the opposite. & Metrics capturing changes in regularity (but not richness and regularity) \\
  Environmental filtering & Position change (``position'') & When an increase in observations' trait similarity happens through some strong abiotic constraints \citep{cornwell2006trait}. For example, some trait combinations become more and more unlikely due to some environmental constraints (i.e. some regions of the trait space become unsuitable). & Metrics capturing changes in position (and richness) \\\\
  Competitive exclusion & Evenness change (``evenness'') & When functionally similar observations compete more intensively with one another than with functionally dissimilar observations (``competitive exclusion principle''; \citealt{hardin1960competitive}). At the extreme, it implies that only dissimilar individuals will coexist (``limiting similarity principle''; \citealt{macarthur1967limiting}). & Metrics capturing changes in divergence (but not richness and regularity) \\\\

@@

For the empirical data, we see again a range of different possible interpretations depending on the metric describing the pattern (Figure \ref{Fig:empirical_results}, Supplementary table 5).
For example, all richness metrics (green; Figure \ref{Fig:empirical_results}) pick up a similar relative increase (i.e., relative to the null stressor) in richness for both the historic and extant datasets.
However, the results are occasionally contrasting between the historical and extant datasets, with a respective decrease and increase with some divergence metrics (e.g. functional dispersion based on dendrograms or hypervolumes).
Finally, some metrics pick up a decrease for both datasets (e.g. functional evenness based on hypervolumes - although the $95$\% confidence intervals overlapped with $0$).
Note that this apparent global increase in most metric values may appear counter intuitive given that $46$\% and $69$\% of species went extinct over the two time periods.
This is due to the scaling of the metrics compared to random equivalent extinctions.
That is, Figure \ref{Fig:empirical_results} is not displaying absolute changes in trait space occupancy but rather changes in trait space occupancy relative to a crude neutral model where all species are equally likely to go extinct.
